Irreducible Components and Dimension of the Springer Fiber of a Hook-Type Slodowy Slice

### 2024-09-03 paper.tex
some fixes.  still at the beginning of 6.7

\begin{lemma}\label{small_centralizer}
    \(\mathfrak{z}_{\gl_n}(f)\) is the set of upper-triangular \(X \in \gl_n\) such that for all \(i,j \in \{1,...,n-1\}\),
    \[X_{i + 1,j + 1} = \frac{j(n - j)}{i(n - i)} X_{ij}.\]
\end{lemma}
\begin{proof}
    Let \(X \in \mathfrak{z}_{\gl_n}(f)\).
    Looking at the definition of \(f\) from the previous section (and zero-padding the matrices), we see that \((fX)_{ij} = i (n - i) X_{i + 1,j}\), and \((Xf)_{ij} = (j - 1)(n - (j - 1)) X_{i, j - 1}\).
    So, for any \(i, j \in \{1,...,n\}\),
    \[i(n - i)X_{i + 1,j} = (j - 1)(n - (j - 1))X_{i, j - 1}.\]
    Taking \(j = 1\), the condition above tells us that for all \(i \geq 2\) we have \(X_{i, 1} = 0\).
    Taking \(j > 1\) and \(i < n\), we get that for all \(i,j \in \{1,...,n-1\}\),
    \[X_{i + 1, j + 1} = \frac{j(n - j)}{i(n - i)} X_{ij}.\]
    So, every \(X \in \mathfrak{z}_{\gl_n}(f)\) is upper triangular and satisfies the condition above.
    Conversely, it is clear that for such \(X\) we have \(fX = Xf\).
\end{proof}

@@

Now, fix any \(w\) and \(r\).
We will find the irreducible components of \(\mathcal{P}_{w,r}\).
These will all happen to be equidimensional (with dimensions independent of \(w\) and \(r\)), so their closures in \(\mathcal{P}\) will be irreducible components of \(\mathcal{P}\).
\par Let 
\[G = \{P \in \GL_m : P X P^{-1} = X\},\]
and
\[G_{wr} = \{A \in G : e_{wr}A = e_{wr}\}.\]
Also, define 
\[\mathcal{Q}_{wr} = \{(A_{e_{wr}, b}, V_\bullet) \in \mathcal{P}_{wr}\}.\]
Let \(G\) act on \(\mathcal{P}_{wr}\) by
\[P \cdot (A_{a,b}, V_\bullet) := ((P, I_n) A_{a, b} (P, I_n)^{-1}, (P, I_n)V_\bullet) = (A_{a P^{-1}, Pb}, (P, I_n) V_\bullet).\]
Note that for any \(x \in \mathcal{Q}_{wr}\), we have \(G_{wr} = \{g \in G : g \cdot x \in \mathcal{Q}_{wr}\}\).
So, by restriction of \(G\) to \(G_{wr}\) and \(\mathcal{P}_{wr}\) to \(\mathcal{Q}_{wr}\), we obtain an action of \(G_{wr}\) on \(\mathcal{Q}_{wr}\).
\par Consider the map \(\varphi_{wr} : \mathcal{Q}_{wr} \times G \to \mathcal{P}_{wr}\) defined by
\[(x, P) \mapsto P \cdot x.\]
Letting \(G_{wr}\) act on \(G\) by \(g \cdot h := hg^{-1}\), we obtain an action of \(G_{wr}\) on \(\mathcal{Q}_{wr} \times G\).

@@

\section{The components of \texorpdfstring{\(\mathcal{Q}\)}{Q}}\label{q_comp}
\subsection{Setup}
Let \(X = J(\lambda) \in \gl_m\).
Let \((e_{ij})_{1 \leq i \leq \ell, 1 \leq j \leq \lambda_i}\) be the standard (Jordan) basis for \(\mathbb{C}^m\).
Let
\[\mathcal{Q} = \{(A_{0,b}, V_\bullet) : \forall i. \; A_{0,b} V_{i + 1} \subseteq V_i\}.\]
In this section we find the irreducible components of \(\mathcal{Q}\).
\par We write \(b_{ij}\) to denote the projection of \(b \in \mathbb{C}^m\) onto \(e_{ij}\).
For each row \(i\), let \(p_i(b) = \max\{j : b_{ij} \neq 0\}\) (by convention, the max of the empty set is zero).
Then set \(q_i(b) = \lambda_i - p_i(b)\).
When it is clear enough from context where the \(b\) is coming from, we will just write \(p_i\) and \(q_i\) instead of \(p_i(b)\) and \(q_i(b)\).
\par Let \(I = \{i_1 < \cdots < i_r\} \subseteq \{1, ..., \ell\}\), and let \((\rho_i)_{i \in I}\) be any function \(I \to \mathbb{N}_{> 0}\) such that (1) \(\rho_i \leq \lambda_i\), (2) \(\rho_i\) is decreasing with \(i\), (3) \(\lambda_i - \rho_i\) is decreasing with \(i\), and (4) \(\rho_i < n\).
For notational convenience---although we assign meaning to neither \(i_0\) nor \(i_{r + 1}\)---we define \(q_{i_0} := n\), and \(p_{i_{r + 1}} := 0\).
Then, we define \(B_{I, (\rho_i)}\) as the set of \(b \in \mathbb{C}^m\) satisfying the following conditions.
\begin{itemize}
    \item For all \(k \in \{1, ..., r\}\), \(p_i = \rho_i\).
    \item For all \(k \in \{0, ..., r\}\), \(p_{i_{k + 1}} = \max_{i : q_i < q_{i_k}} p_i\).
\end{itemize}
Note that for any \(b \in B_{I, (\rho_i)}\) we have \(p_{i_1} > \cdots > p_{i_r} > p_{i_{r + 1}}\), and also \(q_{i_0} > q_{i_1} > \cdots > q_{i_r}\).

@@

\begin{lemma}\label{springer_fiber_dim}
    \[\gamma([\mu_1, ..., \mu_{k + 1}]) = \gamma([0, \lambda_1, ..., \lambda_k]) - \] 
    \[\left[\sum_{i : \lambda_i \geq q_{i_0} + \rho_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^r \sum_{\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} \min(p_{i_k}, \lambda_i - q_{i_k})\right].\]
\end{lemma}
\begin{proof}
    Let \(L = [q_{i_0}, \lambda_1, ..., \lambda_k]\).
    Note that
    \[\mu = [..., q_{i_0} + p_{i_1}, ..., q_{i_1} + p_{i_2}, ..., ..., q_{i_r} + p_{i_{r + 1}}, ...].\]
    Let \(L'\) be the result of taking \(\mu\) and, for each \(x\), replacing one occurence of \(q_{i_x} + p_{i_{x + 1}}\) by \(q_{i_x} + p_{i_x}\); that is,
    \[L' = [..., q_{i_0}, ..., q_{i_1} + p_{i_1}, ..., q_{i_2} + p_{i_2}, ..., q_{i_r} + p_{i_r}].\]
    We can transform \(\mu\) into \(L'\) by just `moving' each \(p_{i_k}\) to the right by \(1 + \#\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}\) slots.
    So,
    \[\gamma(L') - \gamma(\mu) = \sum_{k = 1}^r p_{i_k} (1 + \#\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}) = \]
    \[\sum_{k = 1}^r p_{i_k} \cdot \#\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}.\]
    \par Now we consider how to transform \(L'\) into \(L\).
    First we shift \(q_{i_0}\) to the left by \(\#\{i \notin I : \lambda_i \geq q_{i_0} + p_{i_1}\}\) slots.
    Then we leave \(q_{i_0}\) in place and sort the rest of the list.
    This entails shifting each \(q_{i_x} + p_{i_x}\) to the left by \(\#\{i \notin I : q_{i_x} + p_{i_x} > \lambda_i \geq q_{i_x} + p_{i_{x + 1}}\}\) slots.
    Shifting \(q_{i_x} + p_{i_x}\) to the left one slot, by swapping it with \(\lambda_i\), changes the value of \(\gamma\) by \(\lambda_i - (q_{i_x} + p_{i_x})\).
    To go from \(L'\) to \(L\), we can just make these swaps repeatedly.  
    So,
    \[\gamma(L) - \gamma(L') = \]
    \[\sum_{i \notin I : \lambda_i \geq q_{i_0} + p_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i \notin I : q_{i_k} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} (\lambda_i - (q_{i_k} + p_{i_k})).\]
    \par Now, we put these two results together to get \(\gamma(L) - \gamma(\mu)\).
    \begin{align*}
        \gamma(L) - \gamma(\mu) & = \\
        [\gamma(L) - \gamma(L')] + [\gamma(L') - \gamma(\mu)] & = \\
        \left[\sum_{i : \lambda_i \geq q_{i_0} + p_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i : q_{i_k} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} (\lambda_i - (q_{i_k} + p_{i_k}))\right] & + \\
        \left[\sum_{k = 1}^s \sum_{\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} p_{i_k}\right] & = \\
        \sum_{i : \lambda_i \geq q_{i_0} + p_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_k}\}} p_{i_k} & + \\
        \sum_{k = 1}^s \sum_{i : q_{i_k} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}} (\lambda_i - q_{i_k}) & = \\
        \sum_{i : \lambda_i \geq q_{i_0} + p_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} \min(p_{i_k}, \lambda_i - q_{i_k}) & .
    \end{align*}
    Since \(\gamma(L) = \gamma([0, \lambda_1, ..., \lambda_k])\), the equation above implies the desired result.
\end{proof}

@@

\section{The components of \texorpdfstring{\(\mathcal{P}_{J(\lambda)}\)}{P\_\{J(\textbackslash lambda)\}}}\label{p_comp}
As in section 5, we write \(X = J(\lambda) \in \gl_m\), where \(\lambda = (\lambda_1, ..., \lambda_k)\).
We write \(\mathcal{P} := \mathcal{P}_{J(\lambda)}\), and \(A_{a,b} := A_{J(\lambda), a, b}\).
And as before, \((e_{ij})_{ij}\) and \((f_j)_j\) form the standard basis for \(\mathbb{C}^{m + n}\).
\subsection{The components of \texorpdfstring{\(\mathcal{Q}_{wr}\)}{Q\_\{wr\}}}
Recall from section 5 the varieties
\[\mathcal{Q}_{wr} = \{(A_{e_{wr}, b}, V_\bullet) \in \mathcal{P}\}.\]
Fix any \(w,r\).
\cref{a_zero} tells us that 
\[\mathcal{Q}_{wr} \cong \mathcal{Q}' := \{(A'_{X', 0, b}, V_\bullet) : \forall i. \; A'_{X', 0, b} V_{i + 1} \subseteq V_i\},\]
where \(X' = J(\lambda')\), and \(\lambda' = (\lambda_1, ..., \lambda_w - r, ..., \lambda_k)\), and \(m' = m - r\), and \(n' = n + r\).
\par Let \((\mathcal{Q}'_{I, (\rho_i), \alpha})_{I, (\rho_i), \alpha}\) be the irreducible components of \(\mathcal{Q}'\) give by \cref{Q_comps}.
Write \(\mathcal{Q}_{w,r,I,(\rho_i),\alpha}\) to denote the irreducible component of \(\mathcal{Q}_{wr}\) corresponding to \(\mathcal{Q}'_{I, (\rho_i), \alpha}\) via the isomorphism \(\mathcal{Q}_{wr} \cong \mathcal{Q}'\) of \cref{a_zero}.

@@

\subsection{The varieties \texorpdfstring{\(G_{wr}\)}{G\_\{wr\}} and \texorpdfstring{\(G\)}{G}}
Fix \(w,r\).
Recall from section 5 the groups \(G = \{P \in \GL_m : P^{-1}XP = X\}\) and \(G_{wr} = \{A \in G : e_{wr} A = e_{wr}\}\).
\begin{lemma}\label{g_irred_dim}
    \(G\) is irreducible and has dimension \(\sum_{ij} \min(\lambda_i, \lambda_j)\).
\end{lemma}
\begin{proof}
    The closure of \(G\) in \(\gl_m\) is \(\mathfrak{z}_{\gl_m}(X)\).
    \cref{nilpotent_centralizer} says that \(\mathfrak{z}_{\gl_m}(X)\) is isomorphic to \(\mathbb{C}^{\sum_{ij} \min(\lambda_i, \lambda_j)}\).
\end{proof}

@@

\subsection{The components of \texorpdfstring{\(\mathcal{P}_{wr}\)}{P\_\{wr\}}}
Recall from section 5 the subvarieties \(\mathcal{P}_{wr} \subseteq \mathcal{P}\).
From \cref{principal_bundle} we have the principal \(G_{wr}\)-bundle \(\varphi_{wr} : \mathcal{Q}_{wr} \times G \to \mathcal{P}_{wr}\).
% \par Together, \cref{g_irred_dim} and \cref{gwr_irred_dim} tell us that the irreducible components of \(\mathcal{Q}_{wr} \times G\) are the subvarieties \(\mathcal{Q}_{w,r,I,(\rho_i),\alpha} \times G\).

@@

\subsection{The components of \texorpdfstring{\(\mathcal{P}\)}{P}}
\begin{corollary}\label{p_comps}
    Every irreducible component of \(\mathcal{P}\) is the closure of some subvariety of the form \(\varphi_{wr}(\mathcal{Q}_{w,r,I,(\rho_i),\alpha} \times G)\), and the closure of each subvariety of this form is an irreducible component.
    Each has dimension \(\sum_{i \leq j} \min(\lambda_i, \lambda_j)\).
\end{corollary}
\begin{proof}
    Follows directly from \cref{pwr_comps}.
\end{proof}

\section{The components of \texorpdfstring{\(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\)}{S x\_g N}}\label{sxn_comps}
Recall from \cref{sn_iso} that 
\[S \times_\mathfrak{g} \widetilde{\mathcal{N}} \cong \{(A_{X,a,b}, U_\bullet, V_\bullet) : \forall i. \; XU_{i + 1} \subseteq U_i; \forall i. \; A_{X,a,b} V_{i + 1} \subseteq V_i\}.\]
We defined \(\pi : S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to \mathcal{N}_m\) by \((A_{X,a,b}, U_\bullet, V_\bullet) \mapsto X\), and called \(\pi^{-1}(X)\) the \(n\)-Slodowy-slice Springer fiber at \(X\).
\begin{theorem}\label{springer_fiber_comps}
    \(\pi^{-1}(J(\lambda)) \cong \mathcal{P}_{J(\lambda)} \times X_\lambda\).
    Each irreducible component of \(\pi^{-1}(J(\lambda))\) has dimension \(\sum_{ij} \min(\lambda_i, \lambda_j)\).
\end{theorem}
\begin{proof}
    The isomorphism sends \((A_{X,a,b}, U_\bullet, V_\bullet)\) to \(((A_{X, a, b}, U_\bullet), V_\bullet)\).
    The irreducible components of \(\mathcal{P}_{J(\lambda)}\) are given by \cref{p_comps}.
    Those of \(X_\lambda\) are given by \cref{usual_springer_fiber}.
    Adding the dimensions gives 
    \[\sum_{i \leq j} \min(\lambda_i, \lambda_j) + \sum_{i < j} \min(\lambda_i, \lambda_j) = \sum_{ij} \min(\lambda_i, \lambda_j).\]
\end{proof}

>>>>

\begin{lemma}\label{small_centralizer}
    \(\mathfrak{z}_{\gl_n}(f)\) is the set of upper-triangular \(X \in \gl_n\) such that for all \(i,j \in \{1,...,n-1\}\),
    \[X_{i + 1,j + 1} = \frac{j(n - j)}{i(n - i)} X_{ij}.\]
\end{lemma}
\begin{proof}
    Let \(X \in \mathfrak{z}_{\gl_n}(f)\).
    Looking at the definition of \(f\) from the previous section (and zero-padding the matrices), we see that \((fX)_{ij} = i (n - i) X_{i + 1,j}\), and \((Xf)_{ij} = (j - 1)(n - (j - 1)) X_{i, j - 1}\).
    So, for any \(i, j \in \{1,...,n\}\),
    \[i(n - i)X_{i + 1,j} = (j - 1)(n - (j - 1))X_{i, j - 1}.\]
    Taking \(j = 1\), the condition above says that for all \(i \geq 2\) we have \(X_{i, 1} = 0\).
    Taking \(j > 1\) and \(i < n\), we get that for all \(i,j \in \{1,...,n-1\}\),
    \[X_{i + 1, j + 1} = \frac{j(n - j)}{i(n - i)} X_{ij}.\]
    So, every \(X \in \mathfrak{z}_{\gl_n}(f)\) is upper triangular and satisfies the condition above.
    Conversely, it is clear that for such \(X\) we have \(fX = Xf\).
\end{proof}

@@

Now, fix any \(w\) and \(r\).
We will find the irreducible components of \(\mathcal{P}_{w,r}\).
These will all happen to be equidimensional (with dimensions independent of \(w\) and \(r\)), so their closures in \(\mathcal{P}\) will be irreducible components of \(\mathcal{P}\).
\par Let 
\[G = \{P \in \GL_m : P X P^{-1} = X\},\]
and
\[G_{wr} = \{A \in G : e_{wr}A = e_{wr}\}.\]
Also, define 
\[\mathcal{Q}_{wr} = \{(A_{e_{wr}, b}, V_\bullet) \in \mathcal{P}_{wr}\}.\]
Let \(G\) act on \(\mathcal{P}_{wr}\) by
\[P \cdot (A_{a,b}, V_\bullet) := ((P, I_n) A_{a, b} (P, I_n)^{-1}, (P, I_n)V_\bullet) = (A_{a P^{-1}, Pb}, (P, I_n) V_\bullet).\]
For any \(x \in \mathcal{Q}_{wr}\), we have \(G_{wr} = \{g \in G : g \cdot x \in \mathcal{Q}_{wr}\}\).
So, by restriction of \(G\) to \(G_{wr}\) and \(\mathcal{P}_{wr}\) to \(\mathcal{Q}_{wr}\), we obtain an action of \(G_{wr}\) on \(\mathcal{Q}_{wr}\).
\par Consider the map \(\varphi_{wr} : \mathcal{Q}_{wr} \times G \to \mathcal{P}_{wr}\) defined by
\[(x, P) \mapsto P \cdot x.\]
Letting \(G_{wr}\) act on \(G\) by \(g \cdot h := hg^{-1}\), we obtain an action of \(G_{wr}\) on \(\mathcal{Q}_{wr} \times G\).

@@

\section{The Components of \texorpdfstring{\(\mathcal{Q}\)}{Q}}\label{q_comp}
\subsection{Setup}
Let \(X = J(\lambda) \in \gl_m\).
Let \((e_{ij})_{1 \leq i \leq \ell, 1 \leq j \leq \lambda_i}\) be the standard (Jordan) basis for \(\mathbb{C}^m\).
Let
\[\mathcal{Q} = \{(A_{0,b}, V_\bullet) : \forall i. \; A_{0,b} V_{i + 1} \subseteq V_i\}.\]
In this section we find the irreducible components of \(\mathcal{Q}\).
\par We write \(b_{ij}\) to denote the projection of \(b \in \mathbb{C}^m\) onto \(e_{ij}\).
For each row \(i\), let \(p_i(b) = \max\{j : b_{ij} \neq 0\}\) (by convention, the max of the empty set is zero).
Then set \(q_i(b) = \lambda_i - p_i(b)\).
When it is clear enough from context where the \(b\) is coming from, we will just write \(p_i\) and \(q_i\) instead of \(p_i(b)\) and \(q_i(b)\).
\par Let \(I = \{i_1 < \cdots < i_r\} \subseteq \{1, ..., \ell\}\), and let \((\rho_i)_{i \in I}\) be any function \(I \to \mathbb{N}_{> 0}\) such that (1) \(\rho_i \leq \lambda_i\), (2) \(\rho_i\) is decreasing with \(i\), (3) \(\lambda_i - \rho_i\) is decreasing with \(i\), and (4) \(\rho_i < n\).
For notational convenience---although we assign meaning to neither \(i_0\) nor \(i_{r + 1}\)---we define \(q_{i_0} := n\), and \(p_{i_{r + 1}} := 0\).
Then, we define \(B_{I, (\rho_i)}\) as the set of \(b \in \mathbb{C}^m\) satisfying the following conditions.
\begin{itemize}
    \item For all \(k \in \{1, ..., r\}\), \(p_i = \rho_i\).
    \item For all \(k \in \{0, ..., r\}\), \(p_{i_{k + 1}} = \max_{i : q_i < q_{i_k}} p_i\).
\end{itemize}
For any \(b \in B_{I, (\rho_i)}\) we have \(p_{i_1} > \cdots > p_{i_r} > p_{i_{r + 1}}\), and also \(q_{i_0} > q_{i_1} > \cdots > q_{i_r}\).

@@

\begin{lemma}\label{springer_fiber_dim}
    \[\gamma([\mu_1, ..., \mu_{k + 1}]) = \gamma([0, \lambda_1, ..., \lambda_k]) - \] 
    \[\left[\sum_{i : \lambda_i \geq q_{i_0} + \rho_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^r \sum_{\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} \min(p_{i_k}, \lambda_i - q_{i_k})\right].\]
\end{lemma}
\begin{proof}
    We have
    \[\mu = [..., q_{i_0} + p_{i_1}, ..., q_{i_1} + p_{i_2}, ..., ..., q_{i_r} + p_{i_{r + 1}}, ...].\]
    Let \(L'\) be the result of taking \(\mu\) and, for each \(k\), replacing one occurence of \(q_{i_k} + p_{i_{k + 1}}\) by \(q_{i_k} + p_{i_k}\); that is,
    \[L' = [..., q_{i_0}, ..., q_{i_1} + p_{i_1}, ..., q_{i_2} + p_{i_2}, ..., ..., q_{i_r} + p_{i_r}, ...].\]
    We can transform \(\mu\) into \(L'\) by just `moving' each \(p_{i_k}\) to the right by \(1 + \#\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}\) slots.
    So,
    \[\gamma(L') - \gamma(\mu) = \sum_{k = 1}^r p_{i_k} (1 + \#\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}) = \]
    \[\sum_{k = 1}^r p_{i_k} \cdot \#\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}.\]
    \par Let \(L = [q_{i_0}, \lambda_1, ..., \lambda_k]\).
    Now we consider how to transform \(L'\) into \(L\).
    First we shift \(q_{i_0}\) to the left by \(\#\{i \notin I : \lambda_i \geq q_{i_0} + p_{i_1}\}\) slots.
    Then we leave \(q_{i_0}\) in place and sort the rest of the list.
    This entails shifting each \(q_{i_k} + p_{i_k}\) to the left by \(\#\{i \notin I : q_{i_k} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}\) slots.
    Shifting \(q_{i_k} + p_{i_k}\) to the left one slot, by swapping it with \(\lambda_i\), changes the value of \(\gamma\) by \(\lambda_i - (q_{i_k} + p_{i_k})\).
    To go from \(L'\) to \(L\), we can just make these swaps repeatedly.  
    So,
    \[\gamma(L) - \gamma(L') = \]
    \[\sum_{i \notin I : \lambda_i \geq q_{i_0} + p_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i \notin I : q_{i_k} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} (\lambda_i - (q_{i_k} + p_{i_k})).\]
    \par Now, we put these two results together to get \(\gamma(L) - \gamma(\mu)\).
    \begin{align*}
        \gamma(L) - \gamma(\mu) & = \\
        [\gamma(L) - \gamma(L')] + [\gamma(L') - \gamma(\mu)] & = \\
        \left[\sum_{i : \lambda_i \geq q_{i_0} + p_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i : q_{i_k} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} (\lambda_i - (q_{i_k} + p_{i_k}))\right] & + \\
        \left[\sum_{k = 1}^s \sum_{\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} p_{i_k}\right] & = \\
        \sum_{i : \lambda_i \geq q_{i_0} + p_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_k}\}} p_{i_k} & + \\
        \sum_{k = 1}^s \sum_{i : q_{i_k} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}} (\lambda_i - q_{i_k}) & = \\
        \sum_{i : \lambda_i \geq q_{i_0} + p_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} \min(p_{i_k}, \lambda_i - q_{i_k}) & .
    \end{align*}
    Since \(\gamma(L) = \gamma([0, \lambda_1, ..., \lambda_k])\), the equation above implies the desired result.
\end{proof}

@@

\section{The Components of \texorpdfstring{\(\mathcal{P}_{J(\lambda)}\)}{P\_\{J(\textbackslash lambda)\}}}\label{p_comp}
As in section 5, we write \(X = J(\lambda) \in \gl_m\), where \(\lambda = (\lambda_1, ..., \lambda_k)\).
We write \(\mathcal{P} := \mathcal{P}_{J(\lambda)}\), and \(A_{a,b} := A_{J(\lambda), a, b}\).
And as before, \((e_{ij})_{ij}\) and \((f_j)_j\) form the standard basis for \(\mathbb{C}^{m + n}\).
\subsection{The Components of \texorpdfstring{\(\mathcal{Q}_{wr}\)}{Q\_\{wr\}}}
Recall from section 5 the varieties
\[\mathcal{Q}_{wr} = \{(A_{e_{wr}, b}, V_\bullet) \in \mathcal{P}\}.\]
Fix any \(w,r\).
\cref{a_zero} says that 
\[\mathcal{Q}_{wr} \cong \mathcal{Q}' := \{(A'_{X', 0, b}, V_\bullet) : \forall i. \; A'_{X', 0, b} V_{i + 1} \subseteq V_i\},\]
where \(X' = J(\lambda')\), and \(\lambda' = (\lambda_1, ..., \lambda_w - r, ..., \lambda_k)\), and \(m' = m - r\), and \(n' = n + r\).
\par Let \((\mathcal{Q}'_{I, (\rho_i), \alpha})_{I, (\rho_i), \alpha}\) be the irreducible components of \(\mathcal{Q}'\) given by \cref{Q_comps}.
Write \(\mathcal{Q}_{w,r,I,(\rho_i),\alpha}\) to denote the irreducible component of \(\mathcal{Q}_{wr}\) corresponding to \(\mathcal{Q}'_{I, (\rho_i), \alpha}\) via the isomorphism \(\mathcal{Q}_{wr} \cong \mathcal{Q}'\) of \cref{a_zero}.

@@

\subsection{The Varieties \texorpdfstring{\(G_{wr}\)}{G\_\{wr\}} and \texorpdfstring{\(G\)}{G}}
Fix \(w,r\).
Recall from section 5 the groups \(G = \{P \in \GL_m : P^{-1}XP = X\}\) and \(G_{wr} = \{A \in G : e_{wr} A = e_{wr}\}\).
\begin{lemma}\label{g_irred_dim}
    \(G\) is irreducible and has dimension \(\sum_{ij} \min(\lambda_i, \lambda_j)\).
\end{lemma}
\begin{proof}
    The closure of \(G\) in \(\gl_m\) is \(\mathfrak{z}_{\gl_m}(X)\).
    \cref{nilpotent_centralizer} says that \(\mathfrak{z}_{\gl_m}(X)\) is isomorphic to \(\mathbb{C}^{\sum_{ij} \min(\lambda_i, \lambda_j)}\).
\end{proof}

@@

\subsection{The Components of \texorpdfstring{\(\mathcal{P}_{wr}\)}{P\_\{wr\}}}
Recall from section 5 the subvarieties \(\mathcal{P}_{wr} \subseteq \mathcal{P}\).
From \cref{principal_bundle} we have the principal \(G_{wr}\)-bundle \(\varphi_{wr} : \mathcal{Q}_{wr} \times G \to \mathcal{P}_{wr}\).
% \par Together, \cref{g_irred_dim} and \cref{gwr_irred_dim} tell us that the irreducible components of \(\mathcal{Q}_{wr} \times G\) are the subvarieties \(\mathcal{Q}_{w,r,I,(\rho_i),\alpha} \times G\).

@@

\subsection{The Components of \texorpdfstring{\(\mathcal{P}\)}{P}}
\begin{corollary}\label{p_comps}
    Every irreducible component of \(\mathcal{P}\) is the closure of some subvariety of the form \(\varphi_{wr}(\mathcal{Q}_{w,r,I,(\rho_i),\alpha} \times G)\), and the closure of each subvariety of this form is an irreducible component.
    Each has dimension \(\sum_{i \leq j} \min(\lambda_i, \lambda_j)\).
\end{corollary}
\begin{proof}
    Follows directly from \cref{pwr_comps}.
\end{proof}

\section{The Components of \texorpdfstring{\(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\)}{S x\_g N}}\label{sxn_comps}
Recall from \cref{sn_iso} that 
\[S \times_\mathfrak{g} \widetilde{\mathcal{N}} \cong \{(A_{X,a,b}, U_\bullet, V_\bullet) : \forall i. \; XU_{i + 1} \subseteq U_i; \forall i. \; A_{X,a,b} V_{i + 1} \subseteq V_i\}.\]
We defined \(\pi : S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to \mathcal{N}_m\) by \((A_{X,a,b}, U_\bullet, V_\bullet) \mapsto X\), and called \(\pi^{-1}(X)\) the \(n\)-Slodowy-slice Springer fiber at \(X\).
\begin{theorem}\label{springer_fiber_comps}
    \(\pi^{-1}(J(\lambda)) \cong \mathcal{P}_{J(\lambda)} \times X_\lambda\).
    Each irreducible component of \(\pi^{-1}(J(\lambda))\) has dimension \(\sum_{ij} \min(\lambda_i, \lambda_j)\).
\end{theorem}
\begin{proof}
    The isomorphism sends \((A_{X,a,b}, U_\bullet, V_\bullet)\) to \(((A_{X, a, b}, U_\bullet), V_\bullet)\).
    The irreducible components of \(\mathcal{P}_{J(\lambda)}\) are given by \cref{p_comps}.
    Those of \(X_\lambda\) are given by \cref{usual_springer_fiber}.
    Adding the dimensions gives 
    \[\sum_{i \leq j} \min(\lambda_i, \lambda_j) + \sum_{i < j} \min(\lambda_i, \lambda_j) = \sum_{ij} \min(\lambda_i, \lambda_j).\]
\end{proof}
